---
title: "Tutorial 2"
author: "FR"
date: "9/14/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Tutorial 2
## In this tutorial you will learn:
* How to add algorithm settings / configurations to your runs
* How to restart / or change already existing experiments

Basic setup for the tutorial...
```{r echo=TRUE, results='hide', message=FALSE}
## Load Package
require(ideaBatch)

## Loading your configuration
load(paste0(system.file(package = "ideaBatch"),"/config.rda"))

## Cleaning tutorial folder...
unlink(paste0(idea.config.list$desiredDir, "/Experiments/Tutorials/Tutorial_2"), recursive = TRUE)

## Source Package functions
source(paste0(system.file(package = "ideaBatch"),"/sources.R"))
```

This time we want to add changeable settings to an algorithm.
```{r echo=TRUE, results='hide', message=FALSE}
## Create an Experiment Registry with a Dir-Name and a Sub-Directory for each test.
reg <- ideaMakeRegistry("Tutorials","Tutorial_1") 

## Add Algorithms
addAlgorithm("optimLHD", algorithm_SpotOptimByName("optimLHD", c(-5,-5),c(5,5),
                                                    control = list(funEvals = 100)))
addAlgorithm("cmaesCMAES",algorithm_CMAES(c(-5,-5),c(5,5), control = list("maxit" = 100)))


algorithmConfigs <- list(
    "optimLHD" <- data.frame()
)


## Add Objective Functions
addProblem("Rastr2D", of_smoofByName("Rastrigin",2))


### Add Settings???
### 
### 
### 

## Build Experiments
addExperiments(repls = 10)
```

You can see all configured experiments and their replications with the summarizeExperiments command:
```{r}
summarizeExperiments()
```

The Experiments are started with the 'ideaSubmitJobs' command.
```{r echo=TRUE, results='hide', message=FALSE}
## Submit all jobs to the cluster for evaluation
ideaSubmitJobs(reg)

## Load result list, wait until all jobs are finished.
## Be aware that this will take very long if you have long running jobs! Use with care!
resList <- ideaLoadResultList(reg, waitJobs = T)

## Generate a dataframe out of your results
resDF <- ideaBatch::generateResultDF(resList)
```

```{r echo=TRUE, message=FALSE}
## Generate some plot from the results
anyTimePerformancePlot(resDF[which(resDF$problemName == "Rastr2D"),])
```

## Copy Code:

```{r eval=FALSE}
## Load Package
require(ideaBatch)

## Loading your configuration
load(paste0(system.file(package = "ideaBatch"),"/config.rda"))

## Cleaning tutorial folder...
unlink(paste0(idea.config.list$desiredDir, "/Experiments/Tutorials/Tutorial_1"), recursive = TRUE)

## Source Package functions
source(paste0(system.file(package = "ideaBatch"),"/sources.R"))

## Create an Experiment Registry with a Dir-Name and a Sub-Directory for each test.
reg <- ideaMakeRegistry("Tutorials","Tutorial_1") 

## Add Objective Functions
addProblem("Rosen2D", of_smoofByName("Rosenbrock",2))
addProblem("Rastr2D", of_smoofByName("Rastrigin",2))

## Add Algorithms
addAlgorithm("optimLHD", algorithm_SpotOptimByName("optimLHD", c(-5,-5),c(5,5),
                                                   control = list(funEvals = 100)))
addAlgorithm("cmaesCMAES",algorithm_CMAES(c(-5,-5),c(5,5), control = list("maxit" = 100)))

## Build Experiments
addExperiments(repls = 10)

summarizeExperiments()

## Submit all jobs to the cluster for evaluation
ideaSubmitJobs(reg)

## Load result list, wait until all jobs are finished.
## Be aware that this will take very long if you have long running jobs! Use with care!
resList <- ideaLoadResultList(reg, waitJobs = T)

## Generate a dataframe out of your results
resDF <- ideaBatch::generateResultDF(resList)

## Generate some plot from the results
anyTimePerformancePlot(resDF[which(resDF$problemName == "Rastr2D"),])
```
